\documentclass{article}   % list options between brackets

\usepackage{color}
\usepackage{graphicx}
%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%\usepackage{amsthm}
\usepackage{amsmath}

\usepackage{listings}

\usepackage{hyperref}

\usepackage{systeme}

\def\shownotes{1}
\def\notesinmargins{0}

\ifnum\shownotes=1
\ifnum\notesinmargins=1
\newcommand{\authnote}[2]{\marginpar{\parbox{\marginparwidth}{\tiny %
  \textsf{#1 {\textcolor{blue}{notes: #2}}}}}%
  \textcolor{blue}{\textbf{\dag}}}
\else
\newcommand{\authnote}[2]{
  \textsf{#1 \textcolor{blue}{: #2}}}
\fi
\else
\newcommand{\authnote}[2]{}
\fi

\newcommand{\knote}[1]{{\authnote{\textcolor{green}{kushti notes}}{#1}}}
\newcommand{\mnote}[1]{{\authnote{\textcolor{red}{scalahub notes}}{#1}}}

\usepackage[dvipsnames]{xcolor}
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}


% type user-defined commands here
\usepackage[T1]{fontenc}

\usepackage{flushend}


\newcommand{\ma}{\mathcal{A}}
\newcommand{\mb}{\mathcal{B}}
\newcommand{\he}{\hat{e}}
\newcommand{\sr}{\stackrel}
\newcommand{\ra}{\rightarrow}
\newcommand{\la}{\leftarrow}
\newcommand{\state}{state}

\newcommand{\ignore}[1]{} 
\newcommand{\full}[1]{}
\newcommand{\notfull}[1]{#1}
\newcommand{\rand}{\stackrel{R}{\leftarrow}}
\newcommand{\mypar}[1]{\smallskip\noindent\textbf{#1.}}

\begin{document}

\title{Two-Way Pegged Sidechains On Ergo (ErgoHack Report)}
\author{kushti, soysor}


\maketitle

\begin{abstract}
In this report we outline some ways to implement pegged sidechains on Ergo with smart contract powered transfers, where both main and
  side chains are based on UTXOs and support ErgoTree (in its current form, at the same time, sidechain may support more features).
In such setting, transfer from sidechain and back can be done via on-chain contract, then security issues are reduced to
  sidechain consensus issue only.
\end{abstract}


\section{Introduction}

A sidechain~\cite{back2014enabling} is a secondary blockchain connected to the main blockchain with a two-way peg.
Pegged sidechains enable ERG (native cryptocurrency of the Ergo blockchain) and other Ergo blockchain assets to be
transferred between multiple Ergo-like blockchains. Sidechains can be considered as playgrounds for experimental features,
or scalability solution~(for example, a sidechain may support shielded transactions or other privacy-preserving
techniques), allowing to off-load transaction from the main chain to sidechains.

\subsection{Ergo blockchain details}

We provide relevant Ergo blockchain related information relevant to our constructions here. Prior knowledge of UTXO
accounting model, Bitcoin~\cite{nakamoto2009}, data structures~(and many other topics involved in cryptocurrency design) is needed.
\begin{itemize}
\item{} Ergo has UTXO set commitments, so set of unspent outputs after processing transactions in a block is committed via
authenticated AVL+ tree, with tree digest included into a block header.
\item{} Last headers as well as some fields from upcoming header can be read from a contract.
\end{itemize}

\section{Sidechain Data on the Mainnet}

In this section we consider how sidechain data can be stored on the main-chain. A sidechain progress can be represented in the simplest form as a tuple $(h, T_h, U_h, C_{h})$, where
$h$ is a sidechain height, $T_h$ are state changes (transactions) done in $h$, $U_h$ is digest of AVL+ tree built on top
of UTXO set after processing the changes $T_h$, $C_{h}$ is AVL+ tree which contains all the previous sidechain states in form
of key-value pairs $h \rightarrow hash(h || T_h || U_h || C_{h-1})$.

First of all, we need to write this minimal data somewhere, to read in contracts later. Currently, we can think about two options:

\begin{itemize}
\item{} there's extension section of a block, which contains key $\rightarrow$ value pairs, and root of a Merkle tree built upon the pairs is included into a
block header (and can be read by a contract). We can include different sidechains here, or even a tree built on top of sidechains. The only issue with this approach is that Merkle trees are not supported in ErgoTree/Script yet

\item{} we can just put sidechain data into a box identified by some NFT. Then data can be read via read-only input.
\end{itemize}

\subsection{Sidechain Consensus}


There could be different option how sidechain can make a progress
\begin{itemize}
\item{} merged mining - PoW fields (nonce, solution) to be added to the tuple, and writted on the Ergo blockchain. Then sidechain header would be Ergo block header + extension Merkle path or path to box in UTXO set tree + sidechain tuple with PoW data. Security: subset of Ergo miners (so honest majority amongst them)

\item{} if sidechain data is in a box, we can make the box spendable for an Ergo block miner (by using miner pubkey from context like done in emission contract). Security: subset of Ergo miners (so honest majority amongst them). There could be other options here (multisig etc)
\end{itemize}

\section{Transfers}

In this section we consider how to transfer ERG from main chain to sidechain, to get sERG tokens on the sidechain, how
how to transfer sERGs back, getting ERG on the main chain back.

We assume setting where mainchain data is known to sidechain miners (validators) and so can be used in contracts. It seems
this requirement can be relaxed further though.

There are some assumptions we have for simplifying contracts:
\begin{itemize}
  \item sidechain has no storage rent
  \item sidechain consensus rules require that during input script validatin, for context variable \# 125 only mainchain;
        state digest can be provided
\end{itemize}

Then contracts-powered transfers from main-chain to side-chain and back are done as follows:

\begin{enumerate}
  \item user sends $E$ ERG to a contract which is allowing to unlock them when there is a box on the sidechain with
  at least $E$ sERG locked forever (with ${false}$ contract in simplest case, when there's no storage rent on the sidechain);
  unlock may happen after enough main-chain confirmations.

  \item as mainchain state digest can read in sidechain contracts (in our case, via context variable \# 125 ), sidechain
  contract holding all the sERGs initially, may unlock them when main-chain box is in the UTXO state for enough
  side-chain confirmations.
\end{enumerate}

\section{Security}

As transfers are based on contracts, sidechaining security is reduced to consensus.  \knote{to be continued}

\section{Evaluation}

\knote{Fill with tests data}

\section{Further Work}

\newpage
\bibliography{sources}
\bibliographystyle{ieeetr} 

\end{document}
